\documentclass[12pt,a4paper]{letter}

\usepackage[top=1.5cm]{geometry}
\pagestyle{empty}
\usepackage[british]{datetime2}
\DTMlangsetup[en-GB]{abbr}

\begin{document}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}

Peoplebank & \today \\ %company name
Level 15/108 St Georges Terrace\\
Perth WA 6000\\
Re: FIFO - Desktop Support\\
Attn: Ms. Irene Yam\\

\end{tabular*}

Dear Irene Yam,

I am writing to express my interest in the Desktop Support position at your company. As a highly skilled and experienced Desktop Support professional, I am confident that my skills and expertise make me a strong candidate for the role.\\
\\\\
Work in computer repair and system setup since worked an Information Technology Support Role in National Taichung University of Science and Technology. My experience includes troubleshooting and resolving hardware and software issues, setting up new systems and software.
\\\\
Furthermore, I possess excellent communication skills, which have allowed me to effectively liaise with end-users, colleagues, and other departments. I always endeavor to explain technical information in a clear and concise manner, ensuring that users understand the steps they need to take to resolve their issues.
\\\\
I am excited about the opportunity to bring my technical expertise and problem solving skills to your company and your client. Thank you for considering my application. I look forward to the opportunity to further discuss my qualifications with you.
\\\\
Sincerely,\\\\
Hank Zheng\\
57 Greenacre St\\
Pinjarra WA 6208\\
0452 549 590\\
s90512g@gmail.com
\end{document}
