\documentclass[11pt a4paper]{article}
\usepackage[top=1cm, left=1.5cm, right=1.5cm]{geometry}
\parindent=0pt
\usepackage{fontspec}
\setsansfont{Arial}
\usepackage{fancyhdr} 
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{0452 549 590}
\fancyfoot[C]{57 Greenacre St Pinjarra WA 6208} % 页码
\fancyfoot[R]{s90512g@gmail.com}

\begin{document}
\begin{Huge}
\textbf{Hank Zheng}\\
\end{Huge}

%------Summary------%

\begin{LARGE}
\textbf{Summary
\hrulefill
}
\end{LARGE}

Working in WA since September 2022:  Upon my arrival from Taiwan,\,I have been focused on seeking an employment sponsor to support my Regional Visa requirements to obtain my PR. My intention is to continue working in Australia permanently as  I strive to become an Australian citizens \\

%------Work Experience------%
\begin{LARGE}


\textbf{Work Experience
\hrulefill
}
\end{LARGE}

\textbf{Quality Produce International} - Nov. 2022-Feb. 2023 Canning Vale, WA 

Order Fulfilment\\

\textbf{E Ink Holding Inc.} - Oct. 2020 - Jul. 2022 Hsinchu, Taiwan

Automation Engineer
\begin{itemize}
        \item {Design an Inkjet Printer at the micron level with Mechanical Engineer to make the product}
        \item {Design Systems architecture of Inkjet Printer for  industrial applications}
        \item {Use C\# with WPF to finish Inkjet Printer's function for Motion, Image Process}
\end{itemize}
%---------------------------------------------------------

\textbf{Micro-Star International Co., Ltd.} - Oct. 2019 - Oct. 2020 New Taipei, Taiwan 

Software Engineer
\begin{itemize}
\item {Use C\# with WPF UI to Development Program And with C++ library to Communicate with Monitor to setting property.}
\end{itemize} 
%---------------------------------------------------------
\textbf{National Taichung University of Science and Technology} - Sept. 2015 - Jul. 2019 Taichung, Taiwan

Information Technology Support Role

\begin{itemize}
        \item {Install and configure Windows Systems and Linux for classrooms.}
        \item {Computer hardware repair - CPU, MotherBoard, RAM, HDD, Power supply unit, Graphics Card, and Update BIOS}
        \item {Management VMware server application for commercial use}
        \item {Install and configure Linux server for improvement of computer service and interaction and communication with software}
\end{itemize} 


%------Education------%
\begin{LARGE}
\textbf{Education
\hrulefill
}
\end{LARGE}

\textbf{National Taichung University of Science and Technology} - Taichung, Taiwan\\
Master of Computer Science and Engineering\\
Sep. 2017-Jul. 2019\\

\textbf{National Taichung University of Science and Technology} - Taichung, Taiwan\\
Bachelor of Computer Science and Engineering\\
Sep. 2013-Jul. 2017\\

%------SKILL------%
\begin{LARGE}
\textbf{Skills
\hrulefill\\
}
\end{LARGE}
\large{
\textbf{Computer Hardware Repair} - CPU, MotherBoard, RAM, HDD, Power supply unit, Graphics Card, and Update BIOS\\
\textbf{Information Technology} - Microsoft support Engineer Desktop and Network\\
\textbf{Microsoft} - Windows XP, Windows 7, Windows 10, Windows 11 and Windows Server\\
\textbf{Linux} - Install and Configure Apache, MySQL, PHP, VPN and Docker on Linux\\
\textbf{
Forklift Operation\\
}}

%------Licences and certifications------%
\begin{LARGE}

\textbf{Licences and certifications
\hrulefill\\
}
\end{LARGE}
\textbf{WA High Risk Work Licence} - LF Class  \\
\textbf{WA Drivers Licence} - C Class\\
\textbf{WA Construction Induction White Card}

\end{document}